---
title: "Modeling"
author: "Casey Hansen"
date: "`r Sys.Date()`"
output: pdf_document
---
## Preamble
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(ggplot2)
library(tidyverse)
library(stringr)
library(readxl)
library(readr)
library(modelr)
options(na.action = na.warn)

# libary for color palatte packages - *must* be in quotes
library("RColorBrewer")
```

## Taking a Wild Crack at modeling

```{r echo=TRUE, message=FALSE}
#Upload data, save into dataframe named 'digestion' - add missing code


# Create randomized slopes and y-intercepts
models <- tibble(
  a1 = runif(250, -20, 40),
  a2 = runif(250, -5, 5)
)

# Plot data along with lines created by the randomized slopes and intercepts
ggplot(digestion, aes(prot.1, prot.z)) +
  geom_abline(
    aes(intercept = a1, slope = a2),
    data = models, alpha = 1/4
  ) +
  geom_point()
```

## Step 1: Turn model family into R function

```{r}
# Create function for model
model1 <- function(a, data){
  a[1] + data$prot.1 * a[2]
}

# Run model on digestion data with slope of 1.5, intercept of 7
model1(c(7,1.5),digestion)
```

## Step 2: Using RMS to calculate distance between model and data

```{r}

# Create function to measure distance
measure_distance <- function(mod, data){
  diff <- data$prot.z - model1(mod,data)
  sqrt(mean(diff^2))
}

# Measure distance from previously created model
measure_distance(c(7, 1.5), digestion)

# Measure distance from randomly defined slopes and y-intercepts
# This requires from looping and tibbling (let's just call it magic)
digest_dist <- function(a1, a2) {
  measure_distance(c(a1, a2), digestion)
}

models <- models %>%
  mutate(dist = purrr::map2_dbl(a1, a2, digest_dist))

models
```

## Find 10 best models
```{r}
ggplot(digestion, aes(prot.1, prot.z)) +
  geom_point(size = 1, color = "grey30") +
  geom_abline(aes(intercept = a1, slope = a2, color = -dist),
              data = filter(models, rank(dist) <= 10))
```

## Newton-Raphson search
```{r}
# More magic
best <- optim(c(0,0), measure_distance, data = digestion)
best$par

ggplot(digestion, aes(prot.1, prot.z)) +
  geom_point(size = 2, color = "grey30")+
  geom_abline(intercept = best$par[1], slope = best$par[2])
```

## Predictions

In our case, since our example is linear, the prediction will look the same. But it's important to know how to create them in you're looking for a more complicated function
```{r}
grid <- digestion %>%
  data_grid(prot.1)

# When searching for a linear model, you can also make use of the much simpler 
# lm() function
digest_mod <- lm(prot.z ~ prot.1, data = digestion)

# Here we call on the add_predictions() function from modelr
grid <- grid %>%
  add_predictions(digest_mod)

ggplot(digestion, aes(prot.1)) +
  geom_point(aes(y = prot.z)) +
  geom_line(aes(y = pred), data = grid, color = 'red', size = 1)

```

## Residuals
```{r}
digestion <- digestion %>%
  add_residuals(digest_mod)

ggplot(digestion, aes(resid)) +
  geom_freqpoly(binwidth=0.5)
```

