---
title: "32 - Computational Proteomics"
author: "Adapted from Laurent Gatto, (c) 2019"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("MSnbase")
library(MSnbase)
BiocManager::install("proDA")
library(proDA)
BiocManager::install("msdata")
library(msdata)

library(tidyr)
```

### The iPRG data

This iPRG data is a spiked-in exeriment, where 6 proteins where spiked at different ratios in a Yeast proteome background. Each run was repeated in triplicates and order was randomised. Participants in the study were asked to identify the differentially abundant spiked-in proteins.
```{r}
iprg <- readr::read_csv("http://bit.ly/VisBiomedDataIprgCsv")
print(iprg)
table(iprg$Condition, iprg$TechReplicate)
```

Simplifying the data to keep only the relevant columns, and convert iPRG into a wide format with `tidyr::spread`
```{r}
iprg2 <- iprg[, c(1, 3, 6)]
iprg3 <- spread(iprg2, key = Run, value = Intensity)
```

Verify if there are proteins that haven’t been quantified in some samples.
```{r}
k <- which(is.na(iprg3), arr.ind = dim(iprg3))
k
iprg3[unique(k[, "row"]), ]
```

The opposite operation to `spread` is `gather`, also from the `tidyr` package: Check `iprg4` against `irpg2` - what is the code doing to create these differences?
```{r}
iprg4 <- gather(iprg3, key = Run, value = Intensity, -Protein)
nrow(iprg2)
nrow(iprg4)
nrow(na.omit(iprg4))
iprg5 <- gather(iprg3, key = Run, value = Intensity, -Protein, na.rm = TRUE)
```

