---
title: "Advanced-EDA"
author: "Casey Hansen"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

## Example of plotting a histogram

```{r cars}
ggplot(data = diamonds) + geom_bar(mapping = aes(x=cut))
```

# Plotting mulitple histgrams comparitively using geom_freqpoly()
```{r}
# Select data for diamonds 3 carats or smaller
smaller <- diamonds %>%
     filter(carat<3)

#Plot size histograms from all from each 'cut' category
ggplot(data = smaller, mapping = aes(x = carat, color = cut)) + geom_freqpoly(binwidth=0.1)
```


# Typical values
- Why are there more diamonds at whole carats and common fractions of carats?
- Why are there more diamonds slightly to the right of each peak than there are slight to the left of each peak?
- Why are there no diamonds bigger than 3 carats?
```{r}
ggplot(data = smaller, mapping = aes(x = carat)) + geom_histogram(binwidth = 0.01)
```

# Histogram vs. Density
```{r}
#histogram as lines plot
ggplot(data = diamonds, mapping = aes(x=price)) + geom_freqpoly(mapping = aes(color=cut),binwidth=500)

#Density plot
ggplot(data = diamonds, mapping = aes(x=price,y=..density..)) + geom_freqpoly(mapping = aes(color=cut),binwidth=500)
```
# Heat Map
```{r}
# Counting instances of cut WRT to color
diamonds %>%
  count(color, cut)

# Using the count to create a heat map
diamonds %>%
  count(color, cut) %>%
  ggplot(mapping = aes(x = color, y = cut)) + geom_tile(mapping = aes(fill = n))

```
```{r}
# A much more complex heatmap
# Found at https://stackoverflow.com/questions/25195869/how-to-change-color-palette-of-geom-tile-in-r-ggplot2
ddf = structure(list(yy = c(60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L, 60L, 61L, 62L, 63L, 64L, 65L, 66L, 67L, 
68L, 69L, 70L, 71L, 72L), xx = structure(c(1L, 1L, 1L, 1L, 1L, 
1L, 1L, 1L, 1L, 1L, 1L, 1L, 1L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 2L, 
2L, 2L, 2L, 2L, 2L, 3L, 3L, 3L, 3L, 3L, 3L, 3L, 3L, 3L, 3L, 3L, 
3L, 3L, 4L, 4L, 4L, 4L, 4L, 4L, 4L, 4L, 4L, 4L, 4L, 4L, 4L, 5L, 
5L, 5L, 5L, 5L, 5L, 5L, 5L, 5L, 5L, 5L, 5L, 5L, 6L, 6L, 6L, 6L, 
6L, 6L, 6L, 6L, 6L, 6L, 6L, 6L, 6L, 7L, 7L, 7L, 7L, 7L, 7L, 7L, 
7L, 7L, 7L, 7L, 7L, 7L, 8L, 8L, 8L, 8L, 8L, 8L, 8L, 8L, 8L, 8L, 
8L, 8L, 8L, 9L, 9L, 9L, 9L, 9L, 9L, 9L, 9L, 9L, 9L, 9L, 9L, 9L, 
10L, 10L, 10L, 10L, 10L, 10L, 10L, 10L, 10L, 10L, 10L, 10L, 10L, 
11L, 11L, 11L, 11L, 11L, 11L, 11L, 11L, 11L, 11L, 11L, 11L, 11L, 
12L, 12L, 12L, 12L, 12L, 12L, 12L, 12L, 12L, 12L, 12L, 12L, 12L, 
13L, 13L, 13L, 13L, 13L, 13L, 13L, 13L, 13L, 13L, 13L, 13L, 13L, 
14L, 14L, 14L, 14L, 14L, 14L, 14L, 14L, 14L, 14L, 14L, 14L, 14L, 
15L, 15L, 15L, 15L, 15L, 15L, 15L, 15L, 15L, 15L, 15L, 15L, 15L, 
16L, 16L, 16L, 16L, 16L, 16L, 16L, 16L, 16L, 16L, 16L, 16L, 16L, 
17L, 17L, 17L, 17L, 17L, 17L, 17L, 17L, 17L, 17L, 17L, 17L, 17L, 
18L, 18L, 18L, 18L, 18L, 18L, 18L, 18L, 18L, 18L, 18L, 18L, 18L, 
19L, 19L, 19L, 19L, 19L, 19L, 19L, 19L, 19L, 19L, 19L, 19L, 19L, 
20L, 20L, 20L, 20L, 20L, 20L, 20L, 20L, 20L, 20L, 20L, 20L, 20L, 
21L, 21L, 21L, 21L, 21L, 21L, 21L, 21L, 21L, 21L, 21L, 21L, 21L, 
22L, 22L, 22L, 22L, 22L, 22L, 22L, 22L, 22L, 22L, 22L, 22L, 22L, 
23L, 23L, 23L, 23L, 23L, 23L, 23L, 23L, 23L, 23L, 23L, 23L, 23L, 
24L, 24L, 24L, 24L, 24L, 24L, 24L, 24L, 24L, 24L, 24L, 24L, 24L, 
25L, 25L, 25L, 25L, 25L, 25L, 25L, 25L, 25L, 25L, 25L, 25L, 25L, 
26L, 26L, 26L, 26L, 26L, 26L, 26L, 26L, 26L, 26L, 26L, 26L, 26L, 
27L, 27L, 27L, 27L, 27L, 27L, 27L, 27L, 27L, 27L, 27L, 27L, 27L, 
28L, 28L, 28L, 28L, 28L, 28L, 28L, 28L, 28L, 28L, 28L, 28L, 28L, 
29L, 29L, 29L, 29L, 29L, 29L, 29L, 29L, 29L, 29L, 29L, 29L, 29L, 
30L, 30L, 30L, 30L, 30L, 30L, 30L, 30L, 30L, 30L, 30L, 30L, 30L, 
31L, 31L, 31L, 31L, 31L, 31L, 31L, 31L, 31L, 31L, 31L, 31L, 31L, 
32L, 32L, 32L, 32L, 32L, 32L, 32L, 32L, 32L, 32L, 32L, 32L, 32L, 
33L, 33L, 33L, 33L, 33L, 33L, 33L, 33L, 33L, 33L, 33L, 33L, 33L, 
34L, 34L, 34L, 34L, 34L, 34L, 34L, 34L, 34L, 34L, 34L, 34L, 34L, 
35L, 35L, 35L, 35L, 35L, 35L, 35L, 35L, 35L, 35L, 35L, 35L, 35L, 
36L, 36L, 36L, 36L, 36L, 36L, 36L, 36L, 36L, 36L, 36L, 36L, 36L, 
37L, 37L, 37L, 37L, 37L, 37L, 37L, 37L, 37L, 37L, 37L, 37L, 37L, 
38L, 38L, 38L, 38L, 38L, 38L, 38L, 38L, 38L, 38L, 38L, 38L, 38L, 
39L, 39L, 39L, 39L, 39L, 39L, 39L, 39L, 39L, 39L, 39L, 39L, 39L, 
40L, 40L, 40L, 40L, 40L, 40L, 40L, 40L, 40L, 40L, 40L, 40L, 40L, 
41L, 41L, 41L, 41L, 41L, 41L, 41L, 41L, 41L, 41L, 41L, 41L, 41L, 
42L, 42L, 42L, 42L, 42L, 42L, 42L, 42L, 42L, 42L, 42L, 42L, 42L, 
43L, 43L, 43L, 43L, 43L, 43L, 43L, 43L, 43L, 43L, 43L, 43L, 43L, 
44L, 44L, 44L, 44L, 44L, 44L, 44L, 44L, 44L, 44L, 44L, 44L, 44L, 
45L, 45L, 45L, 45L, 45L, 45L, 45L, 45L, 45L, 45L, 45L, 45L, 45L, 
46L, 46L, 46L, 46L, 46L, 46L, 46L, 46L, 46L, 46L, 46L, 46L, 46L, 
47L, 47L, 47L, 47L, 47L, 47L, 47L, 47L, 47L, 47L, 47L, 47L, 47L, 
48L, 48L, 48L, 48L, 48L, 48L, 48L, 48L, 48L, 48L, 48L, 48L, 48L, 
49L, 49L, 49L, 49L, 49L, 49L, 49L, 49L, 49L, 49L, 49L, 49L, 49L, 
50L, 50L, 50L, 50L, 50L, 50L, 50L, 50L, 50L, 50L, 50L, 50L, 50L, 
51L, 51L, 51L, 51L, 51L, 51L, 51L, 51L, 51L, 51L, 51L, 51L, 51L, 
52L, 52L, 52L, 52L, 52L, 52L, 52L, 52L, 52L, 52L, 52L, 52L, 52L, 
53L, 53L, 53L, 53L, 53L, 53L, 53L, 53L, 53L, 53L, 53L, 53L, 53L, 
54L, 54L, 54L, 54L, 54L, 54L, 54L, 54L, 54L, 54L, 54L, 54L, 54L, 
55L, 55L, 55L, 55L, 55L, 55L, 55L, 55L, 55L, 55L, 55L, 55L, 55L, 
56L, 56L, 56L, 56L, 56L, 56L, 56L, 56L, 56L, 56L, 56L, 56L, 56L, 
57L, 57L, 57L, 57L, 57L, 57L, 57L, 57L, 57L, 57L, 57L, 57L, 57L, 
58L, 58L, 58L, 58L, 58L, 58L, 58L, 58L, 58L, 58L, 58L, 58L, 58L, 
59L, 59L, 59L, 59L, 59L, 59L, 59L, 59L, 59L, 59L, 59L, 59L, 59L, 
60L, 60L, 60L, 60L, 60L, 60L, 60L, 60L, 60L, 60L, 60L, 60L, 60L, 
61L, 61L, 61L, 61L, 61L, 61L, 61L, 61L, 61L, 61L, 61L, 61L, 61L, 
62L, 62L, 62L, 62L, 62L, 62L, 62L, 62L, 62L, 62L, 62L, 62L, 62L, 
63L, 63L, 63L, 63L, 63L, 63L, 63L, 63L, 63L, 63L, 63L, 63L, 63L, 
64L, 64L, 64L, 64L, 64L, 64L, 64L, 64L, 64L, 64L, 64L, 64L, 64L, 
65L, 65L, 65L, 65L, 65L, 65L, 65L, 65L, 65L, 65L, 65L, 65L, 65L, 
66L, 66L, 66L, 66L, 66L, 66L, 66L, 66L, 66L, 66L, 66L, 66L, 66L, 
67L, 67L, 67L, 67L, 67L, 67L, 67L, 67L, 67L, 67L, 67L, 67L, 67L, 
68L, 68L, 68L, 68L, 68L, 68L, 68L, 68L, 68L, 68L, 68L, 68L, 68L, 
69L, 69L, 69L, 69L, 69L, 69L, 69L, 69L, 69L, 69L, 69L, 69L, 69L, 
70L, 70L, 70L, 70L, 70L, 70L, 70L, 70L, 70L, 70L, 70L, 70L, 70L, 
71L, 71L, 71L, 71L, 71L, 71L, 71L, 71L, 71L, 71L, 71L, 71L, 71L, 
72L, 72L, 72L, 72L, 72L, 72L, 72L, 72L, 72L, 72L, 72L, 72L, 72L, 
73L, 73L, 73L, 73L, 73L, 73L, 73L, 73L, 73L, 73L, 73L, 73L, 73L, 
74L, 74L, 74L, 74L, 74L, 74L, 74L, 74L, 74L, 74L, 74L, 74L, 74L, 
75L, 75L, 75L, 75L, 75L, 75L, 75L, 75L, 75L, 75L, 75L, 75L, 75L, 
76L, 76L, 76L, 76L, 76L, 76L, 76L, 76L, 76L, 76L, 76L, 76L, 76L, 
77L, 77L, 77L, 77L, 77L, 77L, 77L, 77L, 77L, 77L, 77L, 77L, 77L, 
78L, 78L, 78L, 78L, 78L, 78L, 78L, 78L, 78L, 78L, 78L, 78L, 78L, 
79L, 79L, 79L, 79L, 79L, 79L, 79L, 79L, 79L, 79L, 79L, 79L, 79L, 
80L, 80L, 80L, 80L, 80L, 80L, 80L, 80L, 80L, 80L, 80L, 80L, 80L, 
81L, 81L, 81L, 81L, 81L, 81L, 81L, 81L, 81L, 81L, 81L, 81L, 81L
), .Label = c("50", "51", "52", "53", "54", "55", "56", "57", 
"58", "59", "60", "61", "62", "63", "64", "65", "66", "67", "68", 
"69", "70", "71", "72", "73", "74", "75", "76", "77", "78", "79", 
"80", "81", "82", "83", "84", "85", "86", "87", "88", "89", "90", 
"91", "92", "93", "94", "95", "96", "97", "98", "99", "100", 
"101", "102", "103", "104", "105", "106", "107", "108", "109", 
"110", "111", "112", "113", "114", "115", "116", "117", "118", 
"119", "120", "121", "122", "123", "124", "125", "126", "127", 
"128", "129", "130"), class = "factor"), zz = c(22, 21, 20, 20, 
19, 18, 18, 17, 17, 16, 16, 15, 15, 22, 21, 21, 20, 19, 19, 18, 
18, 17, 17, 16, 16, 15, 22, 22, 21, 20, 20, 19, 19, 18, 17, 17, 
16, 16, 16, 23, 22, 21, 21, 20, 19, 19, 18, 18, 17, 17, 16, 16, 
23, 22, 22, 21, 20, 20, 19, 19, 18, 18, 17, 17, 16, 24, 23, 22, 
21, 21, 20, 20, 19, 18, 18, 17, 17, 16, 24, 23, 23, 22, 21, 21, 
20, 19, 19, 18, 18, 17, 17, 25, 24, 23, 22, 22, 21, 20, 20, 19, 
19, 18, 18, 17, 25, 24, 23, 23, 22, 21, 21, 20, 19, 19, 18, 18, 
17, 25, 25, 24, 23, 22, 22, 21, 20, 20, 19, 19, 18, 18, 26, 25, 
24, 23, 23, 22, 21, 21, 20, 20, 19, 18, 18, 26, 25, 25, 24, 23, 
22, 22, 21, 20, 20, 19, 19, 18, 27, 26, 25, 24, 23, 23, 22, 21, 
21, 20, 20, 19, 19, 27, 26, 25, 25, 24, 23, 22, 22, 21, 21, 20, 
19, 19, 28, 27, 26, 25, 24, 23, 23, 22, 21, 21, 20, 20, 19, 28, 
27, 26, 25, 25, 24, 23, 22, 22, 21, 21, 20, 19, 28, 27, 27, 26, 
25, 24, 23, 23, 22, 21, 21, 20, 20, 29, 28, 27, 26, 25, 25, 24, 
23, 22, 22, 21, 21, 20, 29, 28, 27, 27, 26, 25, 24, 23, 23, 22, 
22, 21, 20, 30, 29, 28, 27, 26, 25, 25, 24, 23, 22, 22, 21, 21, 
30, 29, 28, 27, 26, 26, 25, 24, 23, 23, 22, 22, 21, 31, 30, 29, 
28, 27, 26, 25, 25, 24, 23, 22, 22, 21, 31, 30, 29, 28, 27, 26, 
26, 25, 24, 23, 23, 22, 22, 31, 30, 29, 29, 28, 27, 26, 25, 24, 
24, 23, 22, 22, 32, 31, 30, 29, 28, 27, 26, 26, 25, 24, 23, 23, 
22, 32, 31, 30, 29, 28, 28, 27, 26, 25, 24, 24, 23, 22, 33, 32, 
31, 30, 29, 28, 27, 26, 25, 25, 24, 23, 23, 33, 32, 31, 30, 29, 
28, 27, 27, 26, 25, 24, 24, 23, 34, 32, 31, 30, 30, 29, 28, 27, 
26, 25, 25, 24, 23, 34, 33, 32, 31, 30, 29, 28, 27, 26, 26, 25, 
24, 24, 34, 33, 32, 31, 30, 29, 28, 28, 27, 26, 25, 25, 24, 35, 
34, 33, 32, 31, 30, 29, 28, 27, 26, 26, 25, 24, 35, 34, 33, 32, 
31, 30, 29, 28, 27, 27, 26, 25, 25, 36, 35, 33, 32, 31, 30, 30, 
29, 28, 27, 26, 26, 25, 36, 35, 34, 33, 32, 31, 30, 29, 28, 27, 
27, 26, 25, 37, 35, 34, 33, 32, 31, 30, 29, 28, 28, 27, 26, 25, 
37, 36, 35, 34, 33, 32, 31, 30, 29, 28, 27, 26, 26, 37, 36, 35, 
34, 33, 32, 31, 30, 29, 28, 28, 27, 26, 38, 37, 35, 34, 33, 32, 
31, 30, 29, 29, 28, 27, 26, 38, 37, 36, 35, 34, 33, 32, 31, 30, 
29, 28, 27, 27, 39, 37, 36, 35, 34, 33, 32, 31, 30, 29, 28, 28, 
27, 39, 38, 37, 36, 34, 33, 32, 31, 31, 30, 29, 28, 27, 40, 38, 
37, 36, 35, 34, 33, 32, 31, 30, 29, 28, 28, 40, 39, 38, 36, 35, 
34, 33, 32, 31, 30, 29, 29, 28, 40, 39, 38, 37, 36, 34, 33, 32, 
32, 31, 30, 29, 28, 41, 40, 38, 37, 36, 35, 34, 33, 32, 31, 30, 
29, 28, 41, 40, 39, 37, 36, 35, 34, 33, 32, 31, 30, 30, 29, 42, 
40, 39, 38, 37, 36, 35, 33, 33, 32, 31, 30, 29, 42, 41, 40, 38, 
37, 36, 35, 34, 33, 32, 31, 30, 29, 43, 41, 40, 39, 37, 36, 35, 
34, 33, 32, 31, 30, 30, 43, 42, 40, 39, 38, 37, 36, 35, 34, 33, 
32, 31, 30, 43, 42, 41, 39, 38, 37, 36, 35, 34, 33, 32, 31, 30, 
44, 42, 41, 40, 39, 37, 36, 35, 34, 33, 32, 31, 30, 44, 43, 42, 
40, 39, 38, 37, 36, 35, 34, 33, 32, 31, 45, 43, 42, 41, 39, 38, 
37, 36, 35, 34, 33, 32, 31, 45, 44, 42, 41, 40, 39, 37, 36, 35, 
34, 33, 32, 31, 46, 44, 43, 41, 40, 39, 38, 37, 36, 35, 34, 33, 
32, 46, 45, 43, 42, 40, 39, 38, 37, 36, 35, 34, 33, 32, 47, 45, 
44, 42, 41, 40, 38, 37, 36, 35, 34, 33, 32, 47, 45, 44, 43, 41, 
40, 39, 38, 37, 35, 34, 34, 33, 47, 46, 44, 43, 42, 40, 39, 38, 
37, 36, 35, 34, 33, 48, 46, 45, 43, 42, 41, 39, 38, 37, 36, 35, 
34, 33, 48, 47, 45, 44, 42, 41, 40, 39, 38, 36, 35, 34, 33, 49, 
47, 46, 44, 43, 41, 40, 39, 38, 37, 36, 35, 34, 49, 47, 46, 45, 
43, 42, 41, 39, 38, 37, 36, 35, 34, 50, 48, 46, 45, 44, 42, 41, 
40, 39, 37, 36, 35, 34, 50, 48, 47, 45, 44, 43, 41, 40, 39, 38, 
37, 36, 35, 50, 49, 47, 46, 44, 43, 42, 40, 39, 38, 37, 36, 35, 
51, 49, 48, 46, 45, 43, 42, 41, 40, 38, 37, 36, 35, 51, 50, 48, 
46, 45, 44, 42, 41, 40, 39, 38, 37, 36, 52, 50, 48, 47, 45, 44, 
43, 41, 40, 39, 38, 37, 36, 52, 50, 49, 47, 46, 44, 43, 42, 41, 
39, 38, 37, 36, 53, 51, 49, 48, 46, 45, 43, 42, 41, 40, 39, 38, 
36, 53, 51, 50, 48, 47, 45, 44, 42, 41, 40, 39, 38, 37, 53, 52, 
50, 48, 47, 45, 44, 43, 42, 40, 39, 38, 37, 54, 52, 50, 49, 47, 
46, 44, 43, 42, 41, 40, 38, 37, 54, 52, 51, 49, 48, 46, 45, 44, 
42, 41, 40, 39, 38, 55, 53, 51, 50, 48, 47, 45, 44, 43, 41, 40, 
39, 38, 55, 53, 52, 50, 48, 47, 46, 44, 43, 42, 40, 39, 38, 56, 
54, 52, 50, 49, 47, 46, 45, 43, 42, 41, 40, 39, 56, 54, 52, 51, 
49, 48, 46, 45, 44, 42, 41, 40, 39)), row.names = c(NA, -1053L
), .Names = c("yy", "xx", "zz"), class = "data.frame")

colors <- colorRampPalette(c("blue", "green", "yellow", "red"))(42)
ggplot(ddf) + geom_tile(aes(x=xx, y=yy, fill=factor(zz))) + 
     scale_fill_manual(values=colors)


```

